---
title: "Homework 3"
output: github_document
---

## Problem 1

I will open a dataset called **instacart**
```{r setup, echo=FALSE, message = FALSE}
library(tidyverse)
library(httr)
library(jsonlite)
library(p8105.datasets)
data("instacart")
```

*About the data set*

This data set provides buyer data of instacart. There are the following variabels: `r names(instacart)`. Further the number of columns in **instacart** is `r ncol(instacart)` and the number of observations is `r nrow(instacart)` This dataset could offer business insight to instacart and its advertisers, like the average hour of the day, which is `r mean(pull(instacart, order_hour_of_day))` (24 hour format).

## Problem 2

I will open a dataset called BRFSS
```{r, echo = FALSE, message = FALSE}

data("brfss_smart2010")

```

I will now format the data to use appropriate variable names

```{r, echo = FALSE, message = FALSE}

brfss_smart2010 = 
    janitor::clean_names(brfss_smart2010)

```

```{r}
names(brfss_smart2010)

head(brfss_smart2010)
```
I will focus on the “Overall Health” topic

```{r}

brfss_smart2010 %>% 
            mutate(response_order = recode(response, 
                          "1" = "Excellent", 
                          "2" = "Very good", 
                          "3" = "Good",
                          "4" = "Fair",
                          "5" = "Poor"))%>%
mutate(response_order =         as.factor(response_order)) %>% 
  arrange(response_order)


```


```{r}
```


```{r}

```

## Problem 3

I will open a 
